---
title: "Stock Predictor"
output: flexdashboard::flex_dashboard
---

```{r}
library(DT)
library(flexdashboard)
library(flextable)
library(forecast)
library(timetk)
library(sweep)
library(forecast)
library(tidyquant)
library(tidyverse)
library(LINselect)
library(tsoutliers)
library(expsmooth)
library(fma)
library(vars)
library(aTSA)
library(xts)
library(forecast)
library(fma)
library(expsmooth)
library(lmtest)
library(tseries)
library(Quandl)
library(fpp);
library(urca)
library(GMDH)
library(dygraphs)
```

```{r}
########################## Tingo  ###############################
tingo_key<-"e2f8a116006a88ab198bd1f00d88c7ded77ff32f"  #Self Provided
```

```{r}
##########################   NNETAR Parameters  ###################
Years_Forecast_History<-3
L <-2 #short term forecast horizon
STFH<-L
RPT <-100 #Repeats
decay_N<-.01  #Low Decay
S_N<-8
PATHS<-2000
length_analysis_short_term <-Years_Forecast_History * 252
```

```{r}
##########################  Functions   #############################

### Get High from Stocks

get_high_R<-function(g) {
  g <-as.xts(g)
  LE <-nrow(g)
  SE <-LE- length_analysis_short_term
  g <-as.numeric(g[SE:LE,2])
  g<- na.fill(g, fill = 0)
  g[is.nan(g)] <- 0
  return(g) 
}

### Get Low from Stocks

get_low_R<-function(g) {
  g <-as.xts(g)
  LE <-nrow(g)
  SE <-LE- length_analysis_short_term
  g <-as.numeric(g[SE:LE,3])
  g<- na.fill(g, fill = 0)
  g[is.nan(g)] <- 0
  return(g) 
}

### GMDH Prediction

GMDHForecast <- function(x, L, LVL, I, LYR,WHT){
  x<-as.ts(x)
  fc <- GMDH::fcast(x, method = "RGMDH", input = I, layer = LYR, f.number = L,
                    level = LVL, tf = "all", weight = WHT, lambda = c(0, 0.01, 0.02, 0.04, 0.08, 0.16,
                                                                      0.32, 0.64, 1.28, 2.56, 5.12, 10.24))
  # GMDH doesn't produce a ts object with correct attributes, so we build it
  end <- tsp(x)[2]
  freq <- frequency(x)
  # Set the correct start, end, and frequency for the ts forecast object
  tsProperties <- c(end + 1 / freq, end + L / freq, freq)
  tsp(fc$mean) <- tsProperties
  tsp(fc$upper) <- tsProperties
  tsp(fc$lower) <- tsProperties
  class(fc) <- "forecast"
  return(fc)
}

### GMDH Accuracy
GMDH_ACC <- function(out.HIGH, out.LOW){
  acc<-accuracy(out.HIGH)
  MAPE_High_GMDH <-acc[5]  #MAPE
  
  acc<-accuracy(out.LOW)
  MAPE_LOW_GMDH <-acc[5]  #MAPE
  
  ### Results GMDH
  accuracy_results_GMDH <-data.frame(MAPE_LOW_GMDH, MAPE_High_GMDH)/100
  colnames(accuracy_results_GMDH)<-c("MAPE_Low_GMDH", "MAPE_High_GMDH")
  accuracy_results_GMDH$MAPE_Low_GMDH <-accuracy_results[1] * mean(as.numeric((out.LOW$mean)))
  accuracy_results_GMDH$MAPE_High_GMDH<-accuracy_results[2] * mean(as.numeric((out.HIGH$mean)))
  print(accuracy_results_GMDH)
  
  gmdh_high<-as.numeric(out.HIGH$mean) - accuracy_results_GMDH$MAPE_High_GMDH
  gmdh_high<-round(gmdh_high, digits=2)
  colnames(gmdh_high)<-c("gmdh_forecast_high")
  
  gmdh_low<-as.numeric(out.LOW$mean) + accuracy_results_GMDH$MAPE_Low_GMDH
  gmdh_low<-round(gmdh_low, digits=2)
  colnames(gmdh_low)<-c("gmdh_forecast_low")
  
  gmdh_pred<-data.frame(gmdh_low,gmdh_high)
  
  return(gmdh_pred)
}


### Main Function

Stock_Predict <- function(x){
  
options(digits=4)
symb <-x
a<-getSymbols(symb, src="tiingo", api.key=tingo_key, auto.assign = FALSE)

x<-as.numeric(a[1:30,1]) 
adf_test <-tseries::adf.test(x)
p_value <-ifelse(adf_test$p.value < .05,"Stationary","Not_Stationary")


HIGH     <-get_high_R(a)
LOW     <-get_low_R(a)

###NNETAR_High
TFIT <-auto.arima(HIGH,test="adf")
FIT <-fitted(TFIT, type="regression")
FCAST <-forecast::forecast(TFIT, h=L)
FCAST <-data.frame(FCAST)
CVA_ARF_H <-as.numeric(FCAST[,1])

FIT <- nnetar(HIGH, size=S_N, repeats = RPT, xreg = FIT, decay = decay_N, lambda = BoxCox.lambda(HIGH))
fit_cv <- CVar(LOW,  size=2)
SD <- sd(fit_cv$residuals, na.rm=TRUE)
myinnovs <- rnorm(STFH*PATHS, mean= 0, sd=SD)
FCAST<- forecast::forecast(FIT, h=L ,PI=TRUE, xreg = CVA_ARF_H, npaths=PATHS, innov=myinnovs)


acc<-accuracy(FIT)
MAPE_High <-acc[5]  #MAPE
fcast_NNETAR_high <-data.frame(FCAST)



###NNETAR_LOW
TFIT <-auto.arima(LOW,test="adf")
FIT <-fitted(TFIT, type="regression")
FCAST <-forecast::forecast(TFIT, h=L)
FCAST <-data.frame(FCAST)
CVA_ARF_L <-as.numeric(FCAST[,1])

FIT<- nnetar(LOW, size=S_N, repeats = RPT, xreg = FIT, decay = decay_N, lambda = BoxCox.lambda(LOW))
fit_cv <- CVar(LOW,  size=2)
SD<- sd(fit_cv$residuals, na.rm=TRUE)
myinnovs <- rnorm(STFH*PATHS, mean= 0, sd=SD)
FCAST<- forecast::forecast(FIT, h=L, PI=TRUE, xreg = CVA_ARF_L, npaths=PATHS, innov=myinnovs)

acc<-accuracy(FIT)
MAPE_LOW <-acc[5]  #MAPE

fcast_NNETAR_low <-data.frame(FCAST)

### Results AAL
accuracy_results <-data.frame(MAPE_LOW, MAPE_High)/100
colnames(accuracy_results)<-c("MAPE_Low", "MAPE_High")
accuracy_results$Error_Low<-accuracy_results$MAPE_Low * mean(fcast_NNETAR_low$Point.Forecast)
accuracy_results$Error_High <-accuracy_results$MAPE_High * mean(fcast_NNETAR_high$Point.Forecast)

out.HIGH <-GMDHForecast(HIGH, L, 80, 15, 5, .9)
out.LOW <-GMDHForecast(LOW, L, 80, 15, 5, .9)


gmdh_point_high<-as.numeric(out.HIGH$mean)
gmdh_point_low<-as.numeric(out.LOW$mean)
point_low<-fcast_NNETAR_low$Point.Forecast
point_high<-fcast_NNETAR_high$Point.Forecast

daily_low<-rbind(gmdh_point_low + point_low)/2
daily_high<-rbind(gmdh_point_high + point_high)/2

tmp<-rbind(daily_low,daily_high)
tmp<-round(tmp, digits=2)
name_space <-t(data.frame("Daily_Low","Daily_High"))
rownames(name_space)<-c()

df<-data.frame(name_space,tmp)

df1<-t(data.frame(accuracy_results$MAPE_Low,accuracy_results$MAPE_High)) *100
rownames(df1)<-c()
df1<-round(df1, digits=2)

df2<-t(data.frame(accuracy_results$Error_Low,accuracy_results$Error_High))
rownames(df2)<-c()
df2<-round(df2, digits=2)


df3<-t(data.frame(symb,symb))
rownames(df3)<-c()

df4<-t(data.frame(p_value,p_value))
rownames(df4)<-c()



df<-data.frame(df3,df,df1,df2,df4)
rownames(df)<-c()
colnames(df)<-c("Stock","Prediction_Type","Next_24","Next_48","MAPE","Apply_Error_Value","Stationary?")

df_rtn<-data.frame(df)
  
  return(df_rtn)
}

```

Page 1 {data-navmenu="EVC"}
==================
    
### EVC

```{r warnings=FALSE, include=FALSE}
DF_EVC<-Stock_Predict("EVC")
```
    
```{r warnings=FALSE}
datatable(DF_EVC)
```

### EVC Chart
```{r warnings=FALSE}
getSymbols("EVC", src="tiingo", api.key=tingo_key)
options(scipen=999)
dygraph(OHLC(EVC), main = "Historical Data") %>% 
dyRangeSelector()
```   



Page 2 {data-navmenu="SALM"}
=====================================     

### SALM
    
```{r warnings=FALSE, include=FALSE}
DF_SALM<-Stock_Predict("SALM")

```
    
```{r warnings=FALSE}
datatable(DF_SALM)
```

### SALM Chart
```{r warnings=FALSE}
getSymbols("SALM", src="tiingo", api.key=tingo_key)
options(scipen=999)
dygraph(OHLC(SALM), main = "Historical Data") %>% 
dyRangeSelector()
``` 

Page 3 {data-navmenu="AAL"}
=====================================     

### AAL
    
```{r warnings=FALSE, include=FALSE}
DF_AAL<-Stock_Predict("AAL")

```
    
```{r warnings=FALSE}
datatable(DF_AAL)
```

### AAL Chart
```{r warnings=FALSE}
getSymbols("AAL", src="tiingo", api.key=tingo_key)
options(scipen=999)
dygraph(OHLC(AAL), main = "Historical Data") %>% 
dyRangeSelector()
```  

Page 4 {data-navmenu="F"}
=====================================     

### F
    
```{r warnings=FALSE, include=FALSE}
DF_F<-Stock_Predict("F")

```
    
```{r warnings=FALSE}
datatable(DF_F)
```

### F Chart
```{r warnings=FALSE}
getSymbols("F", src="tiingo", api.key=tingo_key)
options(scipen=999)
dygraph(OHLC(F), main = "Historical Data") %>% 
dyRangeSelector()
``` 


Page 5 {data-navmenu="SMCI"}
=====================================     

### SLGG
    
```{r warnings=FALSE, include=FALSE}
DF_SMCI<-Stock_Predict("SMCI")

```
    
```{r warnings=FALSE}
datatable(DF_SMCI)
```

### SMCI Chart
```{r warnings=FALSE}
getSymbols("SMCI", src="tiingo", api.key=tingo_key)
options(scipen=999)
dygraph(OHLC(SMCI), main = "Historical Data") %>% 
dyRangeSelector()
```  


Page 6 {data-navmenu="DHT"}
=====================================     

### DHT
    
```{r warnings=FALSE, include=FALSE}
DF_DHT<-Stock_Predict("DHT")

```
    
```{r warnings=FALSE}
datatable(DF_DHT)
```

### DHT Chart
```{r warnings=FALSE}
getSymbols("DHT", src="tiingo", api.key=tingo_key)
dygraph(OHLC(DHT), main = "Historical Data") %>% 
dyRangeSelector()
``` 


Page 7 {data-navmenu="FSM"}
=====================================     

### FSM
    
```{r warnings=FALSE, include=FALSE}
DF_FSM<-Stock_Predict("FSM")
```
    
```{r warnings=FALSE}
datatable(DF_FSM)
```

### FSM Chart
```{r warnings=FALSE}
getSymbols("FSM", src="tiingo", api.key=tingo_key)
options(scipen=999)
dygraph(OHLC(FSM), main = "Historical Data") %>% 
dyRangeSelector()
``` 

Page 8 {data-navmenu="CIK"}
=====================================     

### CIK
    
```{r warnings=FALSE, include=FALSE}
DF_CIK<-Stock_Predict("CIK")

```
    
```{r warnings=FALSE}
datatable(DF_CIK)
```

### CIK Chart
```{r warnings=FALSE}
getSymbols("CIK", src="tiingo", api.key=tingo_key)
options(scipen=999)
dygraph(OHLC(CIK), main = "Historical Data") %>% 
dyRangeSelector()
``` 


Page 9 {data-navmenu="CVA"}
=====================================     

### CVA
    
```{r warnings=FALSE, include=FALSE}
DF_CVA<-Stock_Predict("CVA")
```
    
```{r warnings=FALSE}
datatable(DF_CVA)
```

### CVA Chart
```{r warnings=FALSE}
getSymbols("CVA", src="tiingo", api.key=tingo_key)
options(scipen=999)
dygraph(OHLC(CVA), main = "Historical Data") %>% 
dyRangeSelector()
```


Page 10 {data-navmenu="LUB"}
=====================================     

### LUB
    
```{r warnings=FALSE, include=FALSE}
DF_LUB<-Stock_Predict("LUB")

```
    
```{r warnings=FALSE}
datatable(DF_LUB)
```

### LUB Chart
```{r warnings=FALSE}
getSymbols("LUB", src="tiingo", api.key=tingo_key)
options(scipen=999)
dygraph(OHLC(LUB), main = "Historical Data") %>% 
dyRangeSelector()
```


Page 11 {data-navmenu="RUN"}
=====================================     

### RUN
    
```{r warnings=FALSE, include=FALSE}
DF_RUN<-Stock_Predict("RUN")

```
    
```{r warnings=FALSE}
datatable(DF_RUN)
```

### LUB Chart
```{r warnings=FALSE}
getSymbols("RUN", src="tiingo", api.key=tingo_key)
options(scipen=999)
dygraph(OHLC(RUN), main = "Historical Data") %>% 
dyRangeSelector()
```

